%!TEX root = ../../main.tex
\chapter{Former roomneighbors} \label{chap:former_roomneighbors}

In this chapter we honor all the former roomneighbors that have unfortunately left the dorm already *sniff*.

\section{Room U12: Mona Erbach [? - 2025]}\label{sec:monaE}
Hi, I’m Mona from room U12!

I’m studying medicine and am also involved in some other activities at uni, so I’m not home that often. When I am, I usually like to keep to myself, but you’ll sometimes find me in the kitchen cooking or at our shared dinners.

Since my room is right next to the kitchen, I’d love it if we could keep the noise down there, especially during quiet hours.

Outside of uni, I’m into reading, cycling, and I’m active in the volunteer fire department and youth fire brigade.

\section{Room U07: Stellan Wendt [2022-2025]} \label{sec:stellanW}
\setmydatenumber{Birthdate}{2000}{06}{07}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hi, I am Stellan. I am \myage{} years old and currently doing my Bachelor of Education in English and Pedagogy (more of a thing in German, but you probably will understand once you´ve googled it). I love a good chat in the kitchen and sometimes enjoy a meal that is offered by Robin´s great cooking :)

My Hobbies are quite limited; I usually spend my time with friends or with my girlfriend, either doing something fun, gaming, or watching TV series.

I will not be around for too long in the dorm, but hopefully, we get to know each other before I move out!

See you around! :)