\chapter{The folks around} \label{chap:introductions}
\newcounter{Birthdate}%
\newcounter{CurrentDate}%
\setmydatenumber{CurrentDate}{\the\year}{\the\month}{\the\day}%

Hey, you made it to the chapters! Let's start by introducing ourselves, shall we?

\section{Room U13: Robin Epple} \label{sec:robinE}
\setmydatenumber{Birthdate}{2001}{03}{31}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hi, my name is Robin, and I'm \myage{} years old. I am currently in my computer science master's and work as a web developer besides that. I only partially live in Tübingen since my hometown is closer to my office, so I usually move between the semesters. But during the lecture time, I am sure we'll run into each other at some point!

If you're looking for me, start in the kitchen ;). I love to cook for dinner and always appreciate some company, so if you're interested in joining someday, just react to my announcements in chat! Other than cooking, I love listening to epic music. I am a very passionate BeatSaber player, and I have probably watched the \quotes{How to train your dragon} movies a few times too often \^{}\^{}.

Oh, and one more thing: In my bachelor's, I lived in a flat by myself, that's why I came here with a lot of household equipment. So, if you need something like a screwdriver or a vacuum, feel free to ask, maybe I can help!

I'm looking forward to meeting you!

\section{Room U09: Luke Caputo G.} \label{sec:lucasC}
\setmydatenumber{Birthdate}{2004}{07}{01}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hi everyone, I’m Luke (or Lucas if you prefer), and I’m \myage{} years old! I’m pursuing my bachelor’s degree in English and American Studies with a minor in Computational Linguistics. I also work as a tutor, helping high school students with math and physics.  

While you can often find Robin in the kitchen, I’ll probably be there too—not cooking, but eating Robin’s latest creations. Most evenings, though, you’ll find me at the cinema. I love watching movies and binge-watching TV shows as well. If you hear about a movie being screened in Tübingen, let me know—I’d be glad to join!  

Oh, and I don’t have as much equipment as Robin, but if you need something or want a hand with anything, feel free to ask. I’m looking forward to meeting all of you and making some great memories this semester!

\section{Room U17: Silvy Kurzendorfer} \label{sec:silvyK}
\setmydatenumber{Birthdate}{2007}{01}{21}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hi, I'm Silvy! I'm a German-Canadian in the second semester of my bachelor's in computer science. I'm often out and about. I frequent the gym, doing some combination of weightlifting and combat sports (if you want to join the best Brazillian Jui-Jitsu club in Tubingen, give me a call). I also enjoy coding and music-making. 

Similarly to Lucas, I might not be the greatest cook in this kitchen, but I'm always happy to help out with any issues you might encounter, regardless of if they're sensitive or trivial. I particularly enjoy talking things out over a cup of tea!

Good luck, and see ya later!

\section{Room U03: Andrés Herrera} \label{sec:andresH}
\setmydatenumber{Birthdate}{2005}{05}{14}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hello there, my name is Andrés, and I am \myage{} years old. I am currently studying history and also hang out often with the other cooking neighbours (Lucas, Robin, Silvy, etc.) I’m usually in my room, but you can talk to me; I tend to respond as soon as I’m available. In case you are a Spanish speaker you can ask me for general questions as well, if that works better for you. I also like to watch and review movies; I don’t go to the cinema as regularly as Lucas, but we can chat about it. I like to learn about almost anything and discuss different topics, so feel free to share.

\section{Room U08: Danny Löser} \label{sec:dannyL}
\setmydatenumber{Birthdate}{2004}{04}{10}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hey folks, I'm Daniel, or Danny for short. I am \myage{} years old, and currently, I'm pursuing my bachelor's degree in history with a minor in art history.

Originally from the town of Heilbronn I moved here in late 2023 for my studies. Except for some weekends and during classes, I usually am around the dormitories for most of the day; if you need help, you can always hit me up, and I will gladly lend a hand.

My free time is mainly spent playing video games, reading, writing, playing guitar, watching movies, and listening to music. I mainly play roleplaying or strategy games, as well as well-known games like Minecraft and Counter-Strike. Books I read include a varied assortment of different genres and ages. My guitar collects too much dust, and listing my favorite musicians and movies takes too long, but those are topics I will gladly discuss over a cigarette or whenever you catch me in a talkative mood. In summary, if you have a nerdy hobby, I'll gladly hear you talk about it.

I'm looking forward to meeting you and much luck with your studies.

Yours, Danny.

\section{Room U07: Stellan Wendt} \label{sec:stellanW}
\setmydatenumber{Birthdate}{2000}{06}{07}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hi, I am Stellan. I am \myage{} years old and currently doing my Bachelor of Education in English and Pedagogy (more of a thing in German, but you probably will understand once you´ve googled it). I love a good chat in the kitchen and sometimes enjoy a meal that is offered by Robin´s great cooking :)

My Hobbies are quite limited; I usually spend my time with friends or with my girlfriend, either doing something fun, gaming, or watching TV series.

I will not be around for too long in the dorm, but hopefully, we get to know each other before I move out!

See you around! :)

\section{Room U15: Mohamed H. Y. Abdelnour} \label{sec:mohamedA}
\setmydatenumber{Birthdate}{1997}{02}{21}%
\FPsub\result{\theCurrentDate}{\theBirthdate}
\FPdiv\myage{\result}{365.2425}
\FPtrunc\myage{\myage}{0}

Hello guys, my name is Mohamed. I’m \myage{} years old and studying medicine. I am currently preparing for a very important exam—the first state examination :). I have been living in this dorm since 2023.

Because of my studies, I often don’t have much time for other activities, as there is always a lot to learn ;). However, I still try to do other things from time to time, like going for walks or watching football matches. I also often visit my family in the Black Forest on weekends, where I try to take a break from university life.

You won’t often find me in the kitchen, as I hardly ever cook. But I still look forward to seeing you there, having a chat, and maybe sharing some of my mom’s lovingly cooked food with you <3.